For hundreds of years composers have been creating music using external tools like dice to help them generate something new.
As early as the 18th century the idea of using randomness to help the composing process has been used.
The musical dice game, "Musikalisches Würfelspiel", was used to randomly generate music based on precomposed parts. \cite{MusikalischesWurfelspiel2025}
This is a very basic way of generating music, however by the random nature of the dice it will not be able to create anything coherent and meaningful like a human composer can.
Additionally this process only used precomposed parts which were designed to work together.
If we want to generate everything from scratch we need a way more sophisticated system. 
This is where procedural generation comes into the picute.
If we base the meldoy on something random and then use the conventions and "rules" for melodic composition we might be able to generate music that sounds somewhat coherent.
\\

% ////////// CONTEXT and MOTIVATION

Today the most common way to go about generating music is using \ac{AI} and \ac{LLM}.
This enables anyone to create music, however these models are trained on large data sets and imitates what has come before. 
For this thesis the focus is on the craft of creating music, breaking it down to its very primitive form, only pitches and durations.
This will enable the user to have more control over exactly what is being generated.
However this requires us to create a system and models that capture the essence of how exactly we are to go about contructing the very basic musical ideas. 
It will not depend on large data sets and will create a musical ideas that can be processed into a fully fledged musical idea.

If we are able to solve this problem of creating a good structure and model for this kind of generation we will not only have a solution for musical ideas, but this kind of system can solve many kinds of problems.
\\

% ////////// PROBLEM DESCRIPTION

The problem we want to solve is the problem of creating a coherent system that will be able to generate music that adheres to certain musical principles. In order to do this we need to consider many things, and system design is a big part of this.
When buidling such a program we need to consider what parts it should consist of as well as how they are supposed to interact. \ac{OOP} is a solid way to approach this system design.
\\
% ////////// PROBLEM SOLUTION

The solution will be a system that is modular, easy to modify and generate new music using newly defined constraints or inputs on structure, motifs etc... 




