%equations, bib. \\

This chapter provides the background theory for the project. First we give an overview of procedural generation and some of the different methods used in procedural generation. Then we give an overview of some basic music theory that is necessary to fully grasp the structure of the system. Lastly we cover some about object oriented programming.

\input{Chapters/04Procedural-generation}

\newpage{}
\input{Chapters/04Music-theory}

\newpage{}
\input{Chapters/04Object-oriented-programming}

\newpage{}

\section{Iterative development and the use of \ac{AI}}

  \epigraph{
A major problem in the design of a computer system is that many aspects of system behaviour and performance are not discovered until the system has been built...\cite{zurcherIterativeMultiLevelModeling1968}}{\textit{F.W. Zurcher \\ B. Randell}}

  This project utilizes a from of development called iterative design. This means that I do the project by creating a design, taking notes on what needs to be improved, then starting again with the new knowledge gained in the previous iteration. 

  This sounds like more work, but in reality it leads to an effective workflow. It allows for fast prototyping since we can start programming something straight away, then when the project halts due to the system that has been created is incompatible with the ideas for improving it we take notes on what worked, what is missing, and use this to create a specification for the next iteration. 

  By doing this we maintain active development which doesn't stagnate and we can always create a new iteration when development slows down. After 3-4 iterations we should be able to land on a system that works in a way that we are happy with.

  In addition to doing this iterative development we will attempt to develop using artificial intelligence as a tool for assisting the process. However the first two iterations will be without any \ac{AI}. This is to make sure I understand the domain and make my own decisions of how I want the program to work. By doing this work to begin with I work up knowledge in the field and will be better equipped to understand what the \ac{AI} procudes and make sure that it does what I want it to. Without this knowledge I will not be able to efficienlty grasp the \ac{AI} output and will spend a significant time learning what the \ac{AI} has done. 

I will discuss the use of \ac{AI} and whether it is a tool worth using or if it simply ends up creating more work since we need to manually fix bugs or do prompt engineering 
